\documentclass[paper=a4,fontsize=10pt,DIV=12,BCOR=3mm,pdftex]{scrartcl}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{tikz-cd}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{etaremune}

\setlength\parindent{0pt}
\renewcommand{\labelenumi}{\arabic{enumi}.}
\linespread{1.0}


\begin{document}
\thispagestyle{empty}
{
\centering
\Large \textbf{Finn Bartsch -- Curriculum Vitae} \par
}
\bigskip \par
\textit{E-Mail:}~\href{mailto:f.bartsch@math.ru.nl}{f.bartsch@math.ru.nl} \\
\textit{Website:}~\href{https://f-bartsch.github.io}{f-bartsch.github.io} \\
\textit{Mailing address:}~PO Box 9010, 6500 GL Nijmegen, The Netherlands \\
\textit{Visiting address:}~Office HG03.084, Huygens building, Heyendaalseweg 135, 6525 AJ Nijmegen



\subsection*{Education}
PhD Mathematics, expected graduation Fall 2026 \\
Radboud-Universiteit Nijmegen, 2022-2026 \\
Thesis advisor: Ariyan Javanpeykar \\
~\par

M.~Sc.~Mathematics, obtained in September 2022 \\
Johannes Gutenberg-Universität Mainz, 2020-2022 \\
Thesis advisor: Ariyan Javanpeykar \\
Thesis title: \textit{Varieties with many rational points over function fields} \\
~\par

B.~Sc.~Mathematics, obtained in June 2020 \\
Johannes Gutenberg-Universität Mainz, 2017-2020 \\
Thesis advisor: Manuel Blickle \\
Thesis title: \textit{Delta-Ringe}


\subsection*{Papers}

\begin{etaremune}
\item \href{https://arxiv.org/abs/2512.05345}{\textit{More counterexamples to the Arithmetic Puncturing Problem}} \\
Preprint, submitted (2025).

\item \href{https://arxiv.org/abs/2507.01656}{\textit{The Kobayashi pseudometric in the presence of log-terminal singularities}} \\
Preprint, submitted (2025).

\item \href{https://doi.org/10.1112/blms.70119}{\textit{On the finiteness of maps into simple abelian varieties satisfying certain tangency conditions}} \\
Bulletin of the London Mathematical Society, Volume 57(9), pp. 2723-2730 (2025).

\item \href{https://arxiv.org/abs/2502.09400}{\textit{New examples of geometrically special varieties: K3 surfaces, Enriques surfaces, and algebraic groups}} \\
Preprint, submitted (2025).

\item \href{https://doi.org/10.1112/plms.70108}{\textit{Symmetric products and puncturing Campana-special varieties}} (joint with Ariyan Javanpeykar and Aaron Levin) \\
Proceedings of the London Mathematical Society, Volume 131, Issue 6 (2025).

\item \href{https://arxiv.org/abs/2410.06643}{\textit{The Weakly Special Conjecture contradicts orbifold Mordell, and thus abc}} (joint with Frédéric Campana, Ariyan Javanpeykar, and Olivier Wittenberg) \\
Preprint, submitted (2024).

\item \href{https://doi.org/10.1016/j.indag.2024.10.005}{\textit{Parshin's method and the geometric Bombieri--Lang conjecture}} (joint with Ariyan Javanpeykar) \\
Indagationes Mathematicae, Volume 37, Issue 1 (Special issue dedicated to the memory of Jacob Murre), pp. 271-280 (2026).

\item \href{https://doi.org/10.1112/jlms.70348}{\textit{Weakly-special threefolds and non-density of rational points}} (joint with Ariyan Javanpeykar and Erwan Rousseau) \\
Journal of the London Mathematical Society, Volume 112, Issue 5 (2025).

\item \href{https://doi.org/10.1017/S1474748024000094}{\textit{Kobayashi--Ochiai's finiteness theorem for orbifold pairs of general type}} (joint with Ariyan Javanpeykar) \\
Journal of the Institute of Mathematics of Jussieu, Volume 23(6), pp. 2713-2732 (2024).
\end{etaremune}


\subsection*{Teaching}

\subsubsection*{Radboud-Universiteit Nijmegen}
TA for Riemann Surfaces, Mastermath Course (Spring 2025) \\
TA for Sheaves and Geometry (Autumn 2024) \\
TA for Riemann Surfaces, Mastermath Course (Spring 2024) \\
TA for Galois Theory (Autumn 2023) \\
TA for Riemann Surfaces, Mastermath Course (Spring 2023)

\subsubsection*{Johannes Gutenberg-Universität Mainz}
TA for Algebraische Kurven und Riemannsche Flächen (Summer 2022) \\
TA for Grundlagen der Numerik (Summer 2022) \\
TA for Zahlentheorie (Winter 2021/22) \\
TA for Mathematik für Physiker 3a (Summer 2021) \\
TA for Mathematik für Physiker 2b (Winter 2019/20)



\subsection*{Talks}

\subsubsection*{Research talks}

\textit{Symmetric products and puncturing Campana-special varieties} \\
Séminaire Géométrie et Topologie in Brest. (26th September 2025) \medskip

\textit{Symmetric products and puncturing Campana-special varieties} \\
Algebraic Geometry Seminar in Utrecht. (12th June 2025) \medskip

\textit{Symmetric products and puncturing Campana-special varieties} \\
Arithmetic Geometry in Cabourg. (15th May 2025) \medskip

\textit{Symmetric products and puncturing Campana-special varieties} \\
Diophantine and Rationality Problems in Sofia. (11th March 2025) \medskip

\textit{Kobayashi--Ochiai’s finiteness theorem for Campana pairs of general type} \\
DIAMANT Symposium Spring 2024 in Utrecht. (11th April 2024)

\subsubsection*{Learning seminar talks}

\textit{Fano threefolds} \\
Reading seminar on the Geometric Manin Conjecture. (16th December 2025) \medskip

\textit{Valuative ideals} \\
Intercity Seminar on Resolution of Singularities. (4th April 2025) \medskip

\textit{The stable reduction theorem for curves} \\
Algebraic Geometry Seminar in Nijmegen. (19th November 2024) \medskip

\textit{Points of low degree on smooth projective curves} \\
Algebraic Geometry Seminar in Nijmegen. (22nd October 2024) \medskip

\textit{Parshin's proof of Bombieri--Lang for subvarieties of abelian varieties} \\
Seminar on Lang's Conjectures 2023 in Nijmegen. (1st December 2023) \medskip

\textit{The finiteness theorem of Kobayashi--Ochiai} \\
Seminar on Lang's Conjectures 2023 in Nijmegen. (15th September 2023)


\end{document}